Solving Equation to get A value

### 2018-09-10 solving_A.Rmd
:hammer: Removed useless fcts

# Graphical parameters ---------------------------------------------------------
theme_set(theme_bw(12) +
              theme(axis.text.x = element_text(angle = 45),
                    legend.text = element_text(angle = 45)))

# Graphical functions ----------------------------------------------------------
label_scenar_facets = function(scenar_name) {
    scenar_name %>%
        as.character() %>%
        str_remove("R") %>%
        str_split("A") %>%
        map_chr(~paste0("Growth = ",  .x[1], "%\n",
                        "Compet. = ", .x[2], "%"))
}

facet_scenar = facet_wrap(vars(scenario),
                          labeller = labeller(scenario = label_scenar_facets))

label_compet_env = labeller(compet_status = c(compet = "Competition",
                                              no_compet = "Only intra comp."),
                            env_width     = c(constant = "Constant\nEnv. Filter Strength",
                                              varying  = "Varying\nEnv. Filter Strength"))

# Plot the relationship between species abundances along the environment in the
# different scenarios
fig_abund_env = function(simul_df, simul_label) {
    ggplot(simul_df %>%
               filter(N >= 2), aes(patch_optim, N)) +
        geom_point(shape = ".") +
        geom_smooth() +
        facet_scenar +
        labs(x = "Environmental value",
             y = "Species Abundance (gen. = 150)",
             subtitle = simul_label)
}

# Plot the relationship between the CWM of the different trait along the
# environment for the different scenarios
fig_cwm_env = function(simul_df, simul_label) {
    simul_df %>%
        filter(N >= 2) %>%
        group_by(scenario, patch) %>%
        summarise_at(vars(contains("cwm")), sum, na.rm = TRUE) %>%
        mutate(patch_optim = gsub("patches", "", patch) %>%
                   as.numeric()) %>%
        gather("cwm_name", "cwm_value", contains("cwm")) %>%
        ggplot(aes(patch_optim, cwm_value, color = cwm_name)) +
        geom_point() +
        geom_smooth() +
        facet_scenar +
        scale_color_discrete(labels = c(trait1_cwm = "Trait 1",
                                        trait2_cwm = "Trait 2",
                                        trait3_cwm = "Trait 3")) +
        labs(x = "Environment",
             y = "Community-Weighted Mean (CWM)",
             color = NULL,
             subtitle = simul_label) +
        theme(legend.position = "top")
}

# Plot the relationship between patch CWMs along the environment considering
# total abundance
fig_cwm_env_abund = function(simul_df, simul_label, n_bins = 24,
                             given_trans = "identity") {
    simul_df %>%
        group_by(scenario, patch) %>%
        summarise_at(vars(contains("cwm"), N), sum) %>%
        mutate(patch_optim = gsub("patches", "", patch) %>%
                   as.numeric()) %>%
        gather("cwm_name", "cwm_value", contains("cwm")) %>%
        ungroup() %>%
        ggplot(aes(patch_optim, cwm_value, z = N)) +
        stat_summary_2d(bins = n_bins) +
        facet_grid(vars(scenario), vars(cwm_name),
                   labeller = labeller(scenario = label_scenar_facets,
                                       cwm_name = label_value)) +
        scale_fill_viridis_c(trans = given_trans, option = "E") +
        labs(x = "Environment",
             y = "Community-Weighted Mean (CWM)",
             fill = "Total Abundance",
             subtitle = simul_label) +
        theme(legend.position = "top")
}

# Relationship betwee, species trait values along the enviroment showing their
# local abundances for the different traits considered
fig_ind_landscape = function(simul_df, simul_label, n_bins = 22,
                             given_trans = "identity") {

    simul_df <- simul_df %>%
        select(-contains("cwm")) %>%
        gather("trait_name", "trait_value", contains("trait"))

    simul_df_cwm <- simul_df %>%
        group_by(scenario, patch, trait_name) %>%
        summarise(cwm = weighted.mean(trait_value, N))

    simul_df2 <- left_join(simul_df, simul_df_cwm,
                           by = c("scenario", "patch", "trait_name"))

    ggplot(simul_df2 %>%
               filter(N > 0),
           aes(patch_optim, trait_value, z = N)) +
        stat_summary_2d(geom = "raster", bins = n_bins, interpolate = TRUE) +
        geom_line(aes(patch_optim, cwm, color = "firebrick"), size = 1) +
        facet_grid(vars(scenario), vars(trait_name),
                   labeller = labeller(scenario = label_scenar_facets,
                                       trait_name = function(x) gsub("_", " ",
                                                                     x))) +
        scale_fill_viridis_c(trans = given_trans, option = "E") +
        scale_color_manual(name = "CWM", values = c(firebrick = "grey80"),
                           labels = "") +
        labs(x = "Environment",
             y = "Trait Value",
             fill = "Species Abundance",
             subtitle = simul_label) +
        guides(colour = guide_legend(override.aes = list(size = 1,
                                                         color = "grey50"))) +
        theme(legend.position = "top")
}
```

>>>>

# Graphical parameters ---------------------------------------------------------
theme_set(theme_bw(12) +
              theme(axis.text.x = element_text(angle = 45),
                    legend.text = element_text(angle = 45)))
```
